Supplamental Appendix for ``Out-of-Sample Comparisons of Overfit Models''

### 2014-03-25 appendix.tex
Styling: tweak spacing and font size
- changes the font to 12pt charter instead of 11pt
- changes the margins to 1.25in instead of 1in
- changes to single spacing instead of 1 and a half spacing.

Hopefully these all make the document easier to read; I'll probably
undo them before submission though.

\documentclass[11pt]{article}
\input{setup}

\title{Supplamental Appendix for Out-of-Sample Comparisons of Overfit
  Models}
\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu} \\
  Iowa State University}

@@

Fill in the text...

\begin{figure}
  \centering {\large Simulated Coverage of Recursive One-Sided DMW Interval for
    $\E_T\oosB$} \input{floats/mc-interval-generror1-rec.tex}
\caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
  one-sided interval based on the DMW
  OOS, plotted as a function of the fraction of
  observations used in the test sample, $P/T$.  The solid horizontal
  line denotes the intervals' nominal coverage.}
\label{fig:interval-T}
\end{figure}
\clearpage

\begin{figure}
  \centering {\large Simulated Rejection Probability of Recursive DMW Test Under
    $\E_T \oosB \leq 0$} \input{floats/mc-dmwsize-rec.tex}
  \caption{Simulated rejection probabilities for the DMW
    OOS $t$-test given $\E_T \oosB \leq 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-size}
\end{figure}

\begin{figure}
  \centering {\large Simulated Rejection Probability of Recursive Clark and West
    (2006, 2007) \\ Test Under $\E_T \oosB \leq 0$}
  \input{floats/mc-clarkwestsize-rec.tex}
  \caption{Simulated rejection probabilities for Clark and West's
    (2006, 2007) OOS test statistic given $\E_T \oosB
    \leq 0$ with nominal size 10\%.  Values greater than 10\% indicate
    that the test rejects the benchmark model too often.  The solid
    horizontal line indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
   \label{fig:clarkwest}
\end{figure}

\begin{figure}
  \centering {\large Simulated Rejection Probability of Recursive McCracken
    (2007) Test \\ Under $\E_T \oosB \leq 0$}
  \input{floats/mc-mccrackensize-rec.tex}
  \caption{Simulated rejection probabilities for McCracken's (2007)
    OOS test statistic given $\E_T \oosB \leq 0$ with
    nominal size 10\%.  Values greater than 10\% indicate that the
    test rejects the benchmark model too often.  The solid horizontal
    line indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:mccracken}
\end{figure}

\begin{figure}
  \centering {\large Simulated Rejection Probability of Recursive DMW Test Under
    $\E_T \oosB > 0$} \input{floats/mc-dmwpower-rec.tex}
  \caption{Simulated rejection probabilities for the DMW
    OOS $t$-test given $\E_T \oosB > 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-power}
\end{figure}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

% LocalWords:  McCracken's kilian anatolyev rossi REStud JAppliedEconometrics
% LocalWords:  goyal welch rfs reputational calhoun Berbee's mixingales Rt tS
% LocalWords:  Heteroskedasticity Autocorrelation Tt iT th berbee iS de dx ixz
% LocalWords:  DMW mcleish Rs eq ftestreject lightgray veclen RSQLite zeileis
% LocalWords:  heteroskedasticity hothorn RNews JStatSoftware harrell campbell
% LocalWords:  thompson bivariate Welch's multicollinearity Newey newey tw vw
% LocalWords:  merlevede cltvar dR Scwarz davidson indices lrrrr waldtest Df jt
% LocalWords:  dmw McCracken MSE OLS mse inoue huber elemstatlearning efron sw
% LocalWords:  anova akritas jong normalpart coefpart Jong's rproject rsqlite
% LocalWords:  unrestrictive datasets Heyde's ib oos Mcc MeR StW InK DiM CCS lm
% LocalWords:  ClM CoS ClW GiW GiR GoW Cla HTF Efr BoB AkA AkP DeD Mcl Dej Rde
% LocalWords:  Sar Zeh Zei Har CaT NeW MeP HaH AllRefs Diebold jel Whi RoW brc
% LocalWords:  overrejection overreject fpe JoD iR PeT Giacomini WN Wishart T'V
% LocalWords:  premultiply const overrejects overrejecting BWB Gia Schwarz HHK
% LocalWords:  Haf Anatolyev's nonstochastic T'X Sweave tikzDevice pgfSweave

>>>>

\documentclass[12pt]{article}
\input{setup}

\title{Supplamental Appendix for ``Out-of-Sample Comparisons of
  Overfit Models''}
\author{Gray Calhoun\thanks{email: \protect\url{gcalhoun@iastate.edu}} \\
  Iowa State University}

@@

This appendix presents simulation results that accompany
\cite{Cal:14}. As in the main paper, these simulations were conducted
in R \citep{Rde:10} using the MASS \citep{VeR:02}, Matrix
\citep{BM:13}, rlecuyer \citep{SR:12}, and RSQLite \citep{Jam:10}
packages. Graphs were produced in R using Lattice \citep{Sar:10} and
tikzDevice \citep{ShB:11:0.6.1}.

\nocite{DiM:95,Wes:96,Mcc:07,ClW:06,ClW:07}
\bibliographystyle{abbrvnat}
\bibliography{references}

\begin{figure}\centering
  {\large Coverage of recursive DMW OOS interval in simulations}
  \input{floats/mc-interval-generror1-rec.tex}
  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
    a one-sided interval based on the recursive DMW \oost\ test,
    plotted as a function of the fraction of observations used in the
    test sample, $P/T$.  The solid horizontal line denotes the
    intervals' nominal coverage.}
  \label{fig:interval-T}
\end{figure}

\begin{figure}\centering
  {\large Size of recursive DMW \oost\ test in simulations}
  \input{floats/mc-dmwsize-rec.tex}
  \caption{Simulated rejection probabilities for the recursive DMW
    \oost\ test under the null hypothesis that the benchmark model is
    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
    marked with a solid horizontal line. Values greater than 10\%
    indicate that the test rejects the benchmark model too often.}
  \label{fig:ttest-size}
\end{figure}

\begin{figure}\centering
  {\large Size of recursive Clark-West OOS test in simulations}
  \input{floats/mc-clarkwestsize-rec.tex}
  \caption{Simulated rejection probabilities for Clark and West's
    (2006, 2007) recursive OOS test statistic under the null
    hypothesis that the benchmark model is more accurate, $\E_T \oosB
    \leq 0$. Nominal size is 10\% and is marked with a solid
    horizontal line. Values greater than 10\% indicate that the test
    rejects the benchmark model too often.}
  \label{fig:clarkwest}
\end{figure}

\begin{figure}\centering
  {\large Size of recursive McCracken \oost\ test in simulations}
  \input{floats/mc-mccrackensize-rec.tex}
  \caption{Simulated rejection probabilities for McCracken's (2007)
    recursive \oost\ test under the null hypothesis that the benchmark
    model is more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\%
    and is marked with a solid horizontal line. Values greater than
    10\% indicate that the test rejects the benchmark model too
    often.}
  \label{fig:mccracken}
\end{figure}

\begin{figure}\centering
  {\large Power of recursive DMW \oost\ test in simulations}
  \input{floats/mc-dmwpower-rec.tex}
  \caption{Simulated rejection probabilities for the recursive DMW
    \oost\ test under the alternative that the benchmark model is less
    accurate, $\E_T \oosB > 0$. Nominal size is 10\% and is marked
    with a solid horizontal line. Values greater than 10\% indicate
    that the test rejects the benchmark model too often.}
  \label{fig:ttest-power}
\end{figure}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "appendix"
%%% End:
